A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-14 paper.tex
Updated section 8.

By extracting the dependencies into the external dependency map,
we introduce great freedom for the curator to move, transform, and otherwise
manipulate the dependencies of the artifact without damaging the artifact itself.
For example, it is straightforward for an automated tool to examine
all of the dependencies in the map, download those that are missing,
and then modifiy the map to point to the local copies of the dependencies.

@@

%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. 
%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
\section{Discussion of Data and Software Preservation}

This section concludes the important lessons of data and software preservation and experiment reproduction learnt from this case study. 
The necessity of preservation integration of multiple programs, preservation granularity, how to preserve large data, how to mine data and software dependencies,
the presrvation degree of the original filesystems, the importance of investigating user access model of data and software, will be discussed.

\subsection{Preservation Integration of Multiple Programs}

Different experimenters may execute different analysis
programs on the same dataset using the same or overlapping sets of software.
Generating one new package for each analysis program from scratch is
time-consuming and space-consuming, which makes one data and software
preservation mechanism, that can integrate the preservation requirements of
different analysis programs, become necessary.

@@

To integrate the data and software from multiple analysis programs into one
archive, the concrete information of data and software, such as size, version,
source and the number of files, need to be recorded. 
The packaging
process needs to be re-organized. Packaging utility needs to maintain one list
of current software and data subset already stored in the archive. When one
user utilizes the packaging utility to preserve one program, the
packaging utility scans the script, gets the data and software dependency
part, judges whether each dependency has been inside the package, and only adds
the new data and software into the archive, and updates the package information
and relavant retrieval information.

The architecture of preservation integration of multiple programs is shown in
Figure~\ref{fig:Preservation integration}. Script 1 and Script 2, sharing one
dependency B, belongs two different programs. Without preservation
integration, B will be preserved twice in the archive. To improve the utilization efficiency of storage resources,
preservation integration of multiple programs is necessary. In the archive,
only one copy of B is stored, which is referred by both scripts.

\subsection{Preservation Granularity}

Another important factor of data and software preservation is the choice of
preservation granularity. In our implementation of Solution 4, the preservation granularity is one
file, because Parrot virtual filesystem traps each system call and redirects
the access path of each file. As a result, during the packaging process, each
time only one file can be copied into the target package, which is
low-efficient. However, there are other options of preservation granularity.
The software is generally preserved in the unit of package inside the remote
repository, the packaging process of one experiment can adopt one package as
the unit. In addition, if the size of one whole software repository is small
and the access frequency of each package inside it is high, the granularity can
be set to the whole repository.

\subsection{Preservation of Large Data}

The preservation policy must concern about the size of data. If data size is
small, copying it into one pacakge and transferring it between different
machines is not a bad idea. Howerver, when the size becomes large, copying it
into one package will make the size of the package uncontrollable. In
Figure~\ref{fig:Preservation integration}, the size of C is very large and
easily to be obtained through Internet by different users. Directly referring C
as networked resources is more efficient than preserving it into one package.

\subsection{Mining of Dependencies}

The mining degree of data and software dependencies greatly determines the
repeatability of one experiment. Clear data dependencies is easy to figure
out, but how to figure out implicit data dependencies is complex. The situation
of software dependencies is more complex. The software dependencies include OS,
hardware platform, direct software dependencies and indirect software
dependencies.
The first
three categories are easy to deal with. The acquisition of indirect software
dependencies needs more efforts.

One solution is to treat the computing environment, software environment
and scientific data as one integral entirety and preserve the entirety
completely. The reproduction of one experiment using this solution is easier.
However, the original machine is not only for one special experiment and may
concern a large amount of software and data unrelevant to the experiment. The
time and space overhead of this solution must be considered.

Another solution is to utlize package management
tools, like rpm, pacman, apt, to recursively trace each direct software
dependency and generate one clear dependency graph. With the dependency graph,
the new user can configure the software environment and repeat the experiment.

The third solution is to trace the system calls of the experiment execution process
and record the paths of accessed files, which including the files of software dependencies.
Parrot adopts this solution. Even if git is one software dependency, there is no necessary to install git on the new machine.
All the files to guarantee the accurate execution of git has been copied into the package.

%\subsection{The preservation} When the authors and the programs becomes more
%and more, the whole pool of one repo may be nearly to be preserved. why not
%directly copy the whole repo and preserve it at the begining directly?  Answer:
%we must concern the efficiency of repeating one small and simple program.
\subsection{Preservation Degree of Directory Structure}

Data and software preservation of physics experiments must concern the
preservation degree of the original filesystem.  The three core components of
one filesytem are file, directory and metadata.  The access of files can be
divided into two categories: only access file metadata, like size, ownership,
access authority list, and access both the file content and metadata.  If both
the content and metadata need to be accessed, the whole file must be copies
into the package.  However, if only the metadata of one file is accessed, how
to preserve the file needs to be considered carefully. If the file size
is 1KB or 1MB, preserving the content is acceptable. If the size of one file is
1GB, preserving the whole file just for accessing its metadata is
inefficient.

Directory is one list of files and subdirectories under it. At first, we only
copy the accessed items under one directory and ignored the unaccessed items.
However, some operations on one directory depends on each item under it. For
example, {\tt ls /dirA} is one linux command to list the name of each item under
{\tt /dirA}. Because the directory itself has the name list of items under it, only
the path of the directory is recorded into the namelist in the first phrase of
Solution 4. However, when we repeat the command {\tt ls /dirA} using the preserved package, it returns NULL because none of items under it exists in
the package, the behavior of the whole program will become incorrect
and unpredictable.

To ensure the semantics of the original program, all the items under one directory must be copied
into the package. However, the
time and space overhead appears again. Currently, Solution 4 creates one item
with the same name but the size of zero for each item under {\tt /dirA}. Another
solution is to introduce one database to preserve the metadata of each file and
directory.

\subsection{User Access Model of Data and Software}

The user access module of remote data
and software has a great impact of the preservation mechanism, especially when
we try to integrate the preservation of multiple programs. If all the programs
only refer the original data and software and refuse to modify them, the
preservation is easy and can ignore the data version problem. However, if some
programs try to modify the original data and software to accustom to its own
requirement, the preservation mechanism must provide one way to differentiate
the original data and the special data used in one certain
program. To have a clear understanding of the data access model, more examples
need to be investigated.

>>>>

By extracting the dependencies into the external dependency map,
we introduce great freedom for the curator to move, transform, and otherwise
manipulate the dependencies of the artifact without damaging the artifact itself.
For example, it is straightforward for an automated tool to examine
all of the dependencies in the map, download those that are missing,
and then modifiy the map to point to the local copies of the dependencies.
(Or, in the case of a dependency upon a reliable external archive,
the map file could continue to point to the original source.)

@@

%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. 
%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.

@@

\section{Open Problems}

Figure~\ref{fig:Preservation integration} shows the rough information
architecture of the curation environment that we imagine for complex
scientific software like TauRoast.
Each artifact to be preserved is a package that consists of a top-level
script to invoke the software, a dependency map, and the dependencies
themselves, which may be external to the original program.  The artifacts
are then ingested into the archive, where shared dependencies are stored
only once.  In cases where an artifact has a dependency on a trusted
(or very large) remote archive, the dependency may simply be tracked
instead of ingested. A reearcher that wishes to reproduce a given
result need only refer to the unique identifier of the artifact, and will
be able to automatically extract all of the dependent components of
that artifact.

For example, in Figure~\ref{fig:Preservation integration} Script 1 depends on items A, B, and C.  Items A and B are ingested into the archive, where B is shared with Script 2.  Item C is stored in another trustworthy repository and is tracked rather than ingested.  When Script 1 is exported from the repository, items A and B are exported along with it, while C can be copied or remain remote, according to the end user's choice.

As simple as that picture appears, there are a number of problems that must be solved to get there:

{\bf Measure the Mess or Force Cleanliness?}  Two radically different approachs to dependency tracking are possible.  The first is to allow end users complete freedom to construct their environment as desired, then \emph{measure} what items were actually used.  As we have shown, this is possible, but has significant overheads and does not fully preserve the structure or intent of the end user.   The second approach is to \emph{force} users to work in a clean environment in which no resource can be used until a proper dependency has been declared.  This ensures that all dependencies are known in advance (and made explicit to the end user) but places a variety of restrictions on the user's daily work, and may prevent creative approaches that do not fit within the curator's view of how programs should be structured.  Whether end users will accept the inconvenience of forced cleanliness for the benefits of reproducibility can only be discovered through experiment.

{\bf What is the Granularity of Dependencies?}  Dependencies could be handled
at many different levels of granularity.  In this work, we have shown
how they can be handled at the level of entire repositories or individual files.
Other possible choices might include intermediate-sized software packages
(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in fewer packages,
simpler dependency maps, and more wasted space; smaller granularity results
in complex dependency maps and less wasted space.  A hybrid solution may
be able to combine both by storing large granularity dependencies, but
retain the ability to select sub-items out of objects when efficiency demands it.

{\bf What is the Scope of Reuse?}  We have presented the data preservation
problem as primarily one of accurate reproduction: if a result depends
on running program X, we must be able to run exactly X again.  However,
the goal of scientific reproducibility is rarely limited to running
\emph{precisely} what a predecessor did. Often, the objective is to
change a parameter or a data input in order to see how the result is affected.
To that end, the preservation system must capture enough of the surrounding
material to permit modifications to succeed.  From this perspective,
a larger granularity of preservation is desirable.  A better understanding of
how end users will consume preserved software will help to shape how
software is preserved in the first place.

{\bf How to Detect Dependencies?}  If we allow users to work in uncontrolled
environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
the user's script and extract the repository dependencies.  This is clearly
not a scalable approach.  We then demonstrated an automated method of observing
what individual files are accessed by a program. However, this does
not cover all types of dependencies, particularly those that are networked.
More sophisticated observation techniques could infer higher-level information,
such as the RPM package names of the files accessed, the URLs of remote
repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.

{\bf Keep Source, Binary, or Both?}
